### 2012-03-06 paper.tex
Included the simple corrections from Søren Dahl

Oscillating reactions on single crystals at UHV conditions have been studied extensively and is know to originate from surface reconstructions of the surface during the oscillations\cite{Ertl2008}. It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures also shows oscillatory behavior on single crystals of Pt, Pd and Ir. Recent studies have proposed a mechanism on Pd \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface. CO oxidation oscillations has also been observed on Pt thin films\cite{Lund2000}, in macroscopic flow reactors\cite{Singh2010} and on Pt nanoparticles synthesized from wet chemical synthesis and subsequent annealing \cite{Carlsson2006}. Here we investigate CO oscillations in a microreactor model system on size selected Pt nanoparticles by high sensitivity mass spectrometry.

@@

\section{Results}
An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding. Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$. At O$_2$:CO ratio of $\sim0.08$ and a geometrical Pt coverage of $\sim0.1\%$ light-off occurs at approximately 180\,$^\circ$C. The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating ramp. After the initial light-off the sample is cooled to room temperature. When at room temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur. A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical light-off ramp and the subsequent increase in temperature to achieve sustained oscillations is seen. Often the sample will show oscillations either directly upon light-off or on the falling temperature ramp.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample. After performing a light-off ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place. The non-zero value of CO during high conversion periods is consistent with the expected QMS background signals from CO$_2$ and O$_2$.}
  \label{fgr:initial_treatment}
\end{figure}
Nanoparticles with sizes ranging from 3\,nm to 9\,nm have been tested but 3\,nm particles with a geometrical coverage of 0.1\% of the reactor area gave the most stable oscillations. No consistent dependency on oscillation frequency and duty cycle was found that could be attributed to the size of the particles.

@@

The oscillation frequency becomes more irregular with progressing experiment time as shown in Figure \ref{fgr:extracts}. However, the ratio between CO and CO$_2$ integrated over an full period remains constant throughout the entire experiment time, i.e. the samples maintains a constant overall rate independent of oscillation frequency.

@@

\section{Discussion}
Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the reactor setup itself which due to its small size has timescales on the order of seconds. Furthermore, a series of experiments was performed to exclude the oscillations as an instrumental artifact. Firstly, experiments were performed on larger volume reactor thus increasing the residence time in the reactor. Secondly, the oscillations were reproduced on a comparable but not identical setup. Both of these experiments suggests that the oscillations is a property of the Pt nanoparticles.

@@

In this study Pt nanoparticles were investigated which, compared to a single crystal or a thin film, is a very rough surface. It is to be expected that the particles will initially favor the reduced state. As the reaction runs the gas composition towards the outlet of the reactor will become more oxidizing increasing the oxidation rate of the particles. Gradually, as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the QMS as an increase in CO$_2$ and a decrease in CO. As the CO concentration decreases the light-off temperature will decrease hence approaching the constant temperature of the sample resulting in a steep increase in reactivity. It is important to note that the fraction of oxidized particles needed to achieve full conversion is not known. We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor makes this a challenging task. If not all particles are oxidized at light-off they will now oxidize much faster due to the low CO-concentration. The further increased rate will not be visible in the QMS since the reactor is already in full conversion. As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state. Fewer and fewer oxidized particles will be responsible for the activity increasing the roughing rate of the remaining active particles. Just before the overall activity drops only a fraction of the particles participates in the reaction and the deactivation will happen very suddenly. Once these potentially few particles eventually becomes sufficiently rough they will reduce and lose activity hence completing the oscillation cycle. It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt in excess of $10^{6}$/site/s corresponding to as little as $\sim$300 Pt nanoparticles contributing to the reactivity just before the end of the high-activity cycle.

>>>>

Oscillating reactions on single crystals at UHV conditions have been studied extensively and is know to originate from surface reconstructions of the surface during the oscillations\cite{Ertl2008}. It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures also shows oscillatory behavior on single crystals of Pt, Pd and Ir. Recent studies have proposed a mechanism on Pd \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface formation. CO oxidation oscillations has also been observed on Pt thin films\cite{Lund2000}, in macroscopic flow reactors\cite{Singh2010} and on Pt nanoparticles synthesized from wet chemical synthesis and subsequent annealing \cite{Carlsson2006}. Here we investigate CO oscillations in a microreactor model system on size selected Pt nanoparticles by high sensitivity mass spectrometry.

@@

\section{Results}
An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding. Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$. At CO:O$_2$ ratio of $\sim0.08$ and a geometrical Pt coverage of $\sim0.1\%$ light-off occurs at approximately 180\,$^\circ$C. The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating ramp. After the initial light-off the sample is cooled to room temperature. When at room temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur. A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical light-off ramp and the subsequent increase in temperature to achieve sustained oscillations is seen. Often the sample will show oscillations either directly upon light-off or on the falling temperature ramp.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample. After performing a light-off ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place. The non-zero value of CO during high conversion periods is consistent with the expected QMS background signals from CO$_2$ and O$_2$.}
  \label{fgr:initial_treatment}
\end{figure}
Nanoparticles with sizes ranging from 3\,nm to 9\,nm have been tested but 3\,nm particles with a geometrical coverage of 0.1\% of the reactor area gave the most stable oscillations. No consistent dependency on oscillation frequency and duty cycle was found that could be attributed to the size of the particles.

@@

The oscillation frequency becomes more irregular with progressing experiment time as shown in Figure \ref{fgr:extracts}. However, the ratio between CO and CO$_2$ integrated over an full period remains constant throughout the entire experiment time, i.e. the samples maintains a constant average rate independent of oscillation frequency.

@@

\section{Discussion}
Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the reactor setup itself which due to its small size has timescales on the order of seconds. Furthermore, a series of experiments was performed to exclude the oscillations as an instrumental artifact. Firstly, experiments were performed on larger volume reactor thus increasing the residence time in the reactor. Secondly, the oscillations were reproduced on a comparable but not identical setup. Finally attempts at reproducing the phenomenon on Pt-thin films of comparable covarage did not produce any oscillations. All of these experiments suggests that the oscillations is a true property of the Pt nanoparticles.

@@

In this study Pt nanoparticles were investigated which, compared to a single crystal or a thin film, is a very rough surface. It is to be expected that the particles will initially favor the reduced state. As the reaction runs the gas composition towards the outlet of the reactor will become more oxidizing increasing the oxidation rate of the particles (illustrated in Figure~\ref{fgr:full_oscillation}). Gradually, as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the QMS as an increase in CO$_2$ and a decrease in CO. As the CO concentration decreases the light-off temperature will decrease hence approaching the constant temperature of the sample resulting in a steep increase in reactivity. It is important to note that the fraction of oxidized particles needed to achieve full conversion is not known. We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor makes this a challenging task. If not all particles are oxidized at light-off they will now oxidize much faster due to the low CO-concentration. The further increased rate will not be visible in the QMS since the reactor is already in full conversion. As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state. Fewer and fewer oxidized particles will be responsible for the activity increasing the roughing rate of the remaining active particles. Just before the overall activity drops only a fraction of the particles participates in the reaction and the deactivation will happen very suddenly. Once these potentially few particles eventually becomes sufficiently rough they will reduce and lose activity hence completing the oscillation cycle. It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt in excess of $10^{6}$/site/s corresponding to as little as $\sim$300 Pt nanoparticles contributing to the reactivity just before the end of the high-activity cycle.
